---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

```{r, echo=FALSE, results = 'asis'}
pkg <- "pmml"

source("https://raw.githubusercontent.com/mhahsler/pkg_helpers/main/pkg_helpers.R")
pkg_title(pkg)  
```

## Overview

Export various machine learning and statistical models to PMML and generate data transformations in PMML format.

Supported models include:

- Anomaly Detection
- Association Rules 
- Clustering
- K Nearest Neighbors
- Linear Models
- Naive Bayes Classifiers
- Neural Networks
- Support Vector Machines
- Time Series
- Tree-based Models and Ensembles
- Survival analysis models

For a description of the supported packages, see the vignette: [Supported Packages and Additional Functions](https://mhahsler.r-universe.dev/articles/pmml/packages_and_functions.html).

```{r echo=FALSE, results = 'asis'}
pkg_install(pkg)
```

## Example


```{r example, message=FALSE, warning=FALSE}
library(pmml)

# Build an lm model
iris_lm <- lm(Sepal.Length ~ ., data=iris)

# Convert to pmml
iris_lm_pmml <- pmml(iris_lm)

# The PMML model
iris_lm_pmml

# Write to file: 
# save_pmml(iris_lm_pmml,"iris_lm.pmml")
```


## References
- [DMG PMML 4.4.1 specification](http://dmg.org/pmml/v4-4-1/GeneralStructure.html)
