---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

```{r, echo=FALSE, results = 'asis'}
pkg <- "pmml"

source("https://raw.githubusercontent.com/mhahsler/pkg_helpers/main/pkg_helpers.R")
pkg_title(pkg)  
```

**This is the official home for the R package pmml (starting with version pmml_2.6.0).**
Previous versions can be found at [here.](https://github.com/Cumulocity-IoT/r-pmml)


## Overview

The pmml package lets you train machine learning and statistical models
in R and then export them using the [Predictive Model Markup Language (PMML)](https://en.wikipedia.org/wiki/Predictive_Model_Markup_Language).
Many commercial and open data mining platforms support PMML to exchange models. 
This includes Python's scikit learn, Java, IBM SPSS Modeler, KNIME, 
Microsoft SQL Server, and SAS Enterprise Miner 
(see [complete list](https://dmg.org/pmml/products.html)). 

Supported models include:

- Anomaly Detection
- Association Rules 
- Clustering
- K Nearest Neighbors
- Linear Models
- Naive Bayes Classifiers
- Neural Networks
- Support Vector Machines
- Time Series
- Tree-based Models and Ensembles
- Survival analysis models

Supported packages: 
    [ada](https://CRAN.R-project.org/package=ada),
    [amap](https://CRAN.R-project.org/package=amap),
    [arules](https://CRAN.R-project.org/package=arules),
    [e1071](https://CRAN.R-project.org/package=e1071),
    [forecast](https://CRAN.R-project.org/package=forecast),
    [gbm](https://CRAN.R-project.org/package=gbm),
    [glmnet](https://CRAN.R-project.org/package=glmnet),
    [isofor](https://github.com/gravesee/isofor),
    [kernlab](https://CRAN.R-project.org/package=kernlab),
    [neighbr](https://CRAN.R-project.org/package=neighbr),
    stats,
    [nnet](https://CRAN.R-project.org/package=nnet),
    [randomForest](https://CRAN.R-project.org/package=randomForest),
    [rpart](https://CRAN.R-project.org/package=rpart),
    [survival](https://CRAN.R-project.org/package=survival),
    [xgboost](https://CRAN.R-project.org/package=xgboost)

For a description of the supported packages, see the vignette: [Supported Packages and Additional Functions](https://mhahsler.r-universe.dev/articles/pmml/packages_and_functions.html).

## Related Packages

### Java
The Java library [JMML](https://github.com/jpmml) 
can be used to read and execute models stored in PMML format. 
An R interface to the library to create PMML models is called [r2pmml](https://CRAN.R-project.org/package=r2pmml) and available from CRAN.
An R interface for the evaluator, called [jpmml](https://github.com/jpmml/jpmml-evaluator-r),
can be installed from Github.

### Python
[sklearn-pmml-model](https://github.com/iamDecode/sklearn-pmml-model)
can import models trained on R into Python's scikit-learn framework.


```{r echo=FALSE, results = 'asis'}
pkg_install(pkg)
```

## Example


```{r example, message=FALSE, warning=FALSE}
library(pmml)

# Build an lm model
iris_lm <- lm(Sepal.Length ~ ., data=iris)

# Convert to pmml
iris_lm_pmml <- pmml(iris_lm)

# The PMML model
iris_lm_pmml

# Write to file: 
# save_pmml(iris_lm_pmml,"iris_lm.pmml")
```

## References
- [DMG PMML 4.4.1 specification](https://dmg.org/pmml/v4-4-1/GeneralStructure.html)
