---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

```{r, echo=FALSE, results = 'asis'}
pkg <- "pmml"

source("https://raw.githubusercontent.com/mhahsler/pkg_helpers/main/pkg_helpers.R")
pkg_title(pkg)  
```

## Overview

Export various machine learning and statistical models to PMML and generate data transformations in PMML format.
Many commercial and open data mining plattforms support PMML. This includes IBM SPSS Modeler, KNIME, Microsoft SQL Server,
and SAS Enterprise Miner (see [complete list](https://dmg.org/pmml/products.html)). 

Supported models include:

- Anomaly Detection
- Association Rules 
- Clustering
- K Nearest Neighbors
- Linear Models
- Naive Bayes Classifiers
- Neural Networks
- Support Vector Machines
- Time Series
- Tree-based Models and Ensembles
- Survival analysis models

Supported packages: 
    [ada](https://CRAN.R-project.org/package=ada),
    [amap](https://CRAN.R-project.org/package=amap),
    [arules](https://CRAN.R-project.org/package=arules),
    [e1071](https://CRAN.R-project.org/package=e1071),
    [forecast](https://CRAN.R-project.org/package=forecast),
    [gbm](https://CRAN.R-project.org/package=gbm),
    [glmnet](https://CRAN.R-project.org/package=glmnet),
    [isofor](https://github.com/gravesee/isofor),
    [kernlab](https://CRAN.R-project.org/package=kernlab),
    [neighbr](https://CRAN.R-project.org/package=neighbr),
    stats,
    [nnet](https://CRAN.R-project.org/package=nnet),
    [randomForest](https://CRAN.R-project.org/package=randomForest),
    [rpart](https://CRAN.R-project.org/package=rpart),
    [survival](https://CRAN.R-project.org/package=survival),
    [xgboost](https://CRAN.R-project.org/package=xgboost)

For a description of the supported packages, see the vignette: [Supported Packages and Additional Functions](https://mhahsler.r-universe.dev/articles/pmml/packages_and_functions.html).

## Related Packages

The Java library [JMML](https://github.com/jpmml) provides an R interface to create PMML
models called [r2pmml]() available from CRAN and an evaluator [jpmml](https://github.com/jpmml/jpmml-evaluator-r) which
can be installed from Github.


```{r echo=FALSE, results = 'asis'}
pkg_install(pkg)
```

## Example


```{r example, message=FALSE, warning=FALSE}
library(pmml)

# Build an lm model
iris_lm <- lm(Sepal.Length ~ ., data=iris)

# Convert to pmml
iris_lm_pmml <- pmml(iris_lm)

# The PMML model
iris_lm_pmml

# Write to file: 
# save_pmml(iris_lm_pmml,"iris_lm.pmml")
```


## References
- [DMG PMML 4.4.1 specification](http://dmg.org/pmml/v4-4-1/GeneralStructure.html)
